---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarizeColByGroup

<!-- badges: start -->
<!-- badges: end -->

The goal of summarizeColByGroup is to provide a method for grouping a data by a specified column and calculating statistics for another specified column. With this package, users can quickly calculate group-wise statistics like average, maximum, and minimum.

## Installation

You can install the development version of summarizeColByGroup from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/summarizeColByGroup")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(summarizeColByGroup)
library(dplyr)
data <- data.frame(
  group = c("a", "b", "b"),
  summary = c(1, 2, 3)
)
summarize_col_by_group(data, group_col = "group", summary_col = "summary")
```
